\simname 2.0 User's Guide

### 2008-10-03 doc/manual.tex
Fixed a memory corruption in the separable allocator. Still does not function correctly though.
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@734 ce7aba0d-9f81-40a6-a495-cecae84b0515
restore unix line endings
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@737 ce7aba0d-9f81-40a6-a495-cecae84b0515
minor updates
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@738 ce7aba0d-9f81-40a6-a495-cecae84b0515

\author{Ted Jiang, Brian Towles, George Michelogiannakis and William J. Dally}
\title{\simname 2.0 User's Guide}

@@

@@

\item[max\_size] Maximum-size matching. 
\item[islip] iSLIP separable allocator.
\item[pim] Parallel iterative matching separable allocator.
\item[loa] Lonely output allocator.
\item[wavefront] Wavefront matching.
\item[select] Priority-based allocator.  Allocation is performed as in
iSLIP, but with preference towards higher priority packets (see
\texttt{priority} option in Section~\ref{sec:traffic}).

>>>>

\author{Ted Jiang, George Michelogiannakis, Daniel Becker, Brian Towles and William J. Dally}
\title{\simname 2.0 User's Guide}

@@

\subsubsection{The NoC router}
\label{sec:noc_router}

The NoC router (\texttt{router = noc}) is a simplified variant of the input-queued router. It does not support input or output speedup. Also, it does not support multi-cycle allocation, but does support output-first allocation.

@@

\item[max\_size] Maximum-size matching. 
\item[islip] iSLIP separable allocator.
\item[pim] Parallel iterative matching separable allocator.
\item[loa] Lonely output allocator.
\item[wavefront] Wavefront allocator.
\item[matrix] Separable input-first allocator built from matrix arbiters.
\item[round\_robin] Separable input-first allocator built from round-robin arbiters.
\item[select] Priority-based allocator.  Allocation is performed as in
iSLIP, but with preference towards higher priority packets (see
\texttt{priority} option in Section~\ref{sec:traffic}).
